Cosmic web correlations with the shape, spin and peculiar velocties of dark matter halos

### 2013-11-06 paper/main.tex
reference updated

\begin{figure*}
\includegraphics[width=0.80\textwidth]{Fig3.pdf}
\caption{Median of $\cos\theta$ quantifying the angular momentum
  alingment for the Vweb (left) and the Tweb (right) at two different
  grid resolutions. In the upper (lower)  panels the angle $\theta$ is
  measured between the first (third) eivenvector and the angular
  momentum vector.
  \label{fig:spin_alignment}
} 
\end{figure*}

@@

Figure \ref{fig:spin_alignnment} shows the results as a function of
the halo mass. In the case of the V-web the trends can be summarized
as follows. Low mass halos $10^{12}$\hMsun do not show any
preferential alignment with the cosmic web. Halos more massive than
this threshold have their spin slightly perpendicular to the
direction defined by the first eigenvector (defining sheets) and
uncorrelated to the third eigenvector (filament direction). This
translates into a weak tendency for the spin to lie on the
sheet-plane.

>>>>

\begin{figure*}
\includegraphics[width=0.80\textwidth]{Fig3.pdf}
\caption{Median of $\cos\theta$ quantifying the angular momentum
  alingment for the Vweb (left) and the Tweb (right) at two different
  grid resolutions. In the upper (lower)  panels the angle $\theta$ is
  measured between the first (third) eivenvector and the angular
  momentum vector.\label{fig:spin_alignment}} 
\end{figure*}

@@

Figure \ref{fig:spin_alignment} shows the results as a function of
the halo mass. In the case of the V-web the trends can be summarized
as follows. Low mass halos $10^{12}$\hMsun do not show any
preferential alignment with the cosmic web. Halos more massive than
this threshold have their spin slightly perpendicular to the
direction defined by the first eigenvector (defining sheets) and
uncorrelated to the third eigenvector (filament direction). This
translates into a weak tendency for the spin to lie on the
sheet-plane.
